\newpage
\chapter{Project Evaluation}
\label{chap:evaluation}
% provide feedback about the project course: what was good/fun/etc.?, what did you learn?, what didn't work well?, what can be improved for future projects?, other comments...
%This is mainly for feedback to Thomas, Kjell and LTU.

\section{Overall Project Conclusion}
%Final budget status
%What project goals were achieved?
%
The U-SPACE project has demonstrated the student design of a battery powered airship capable of forward propulsion and steering, collecting and downlink of housekeeping data as well as supporting a small scientific payload (camera). Furthermore, it confirms the plausibility of having a completely solar powered airship also when considering the extremely limited lifting mass of the blimp used for the initial test flight.
%
%
\section{Pedro}
In general I am quite satisfied with how the project course turned out. I am very satisfied with the group of people I had to work with and I think it has been a very useful experience for the future. 
However I cannot help but feeling that the coordinators of the project, i.e. whoever is in charge of the decision regarding budgets, reports, ECTS distribution and so on, did not had a well-defined protocol for this course. Because of this I think we wasted a lot of time waiting for answers that should already be clear the moment the university is offering this kind of course. The worst of all is that we wasted the entire previous summer semester because of this. Of course money is money, which is always the main issue, but after all we were a big group of people that just wanted to work. I think that if the university is offering this possibility, the process once the group has presented its ideas properly in a PDR should be a hundred times swifter in case the project is approved. 
But forgetting all the bureaucratic BS, I think the people at LTU Kiruna and IRF were always available to lend us a hand, even when sometimes it was not even their duty and that I really appreciate and I am very thankful for.
%
%
\section{Omair}
It was an interesting and challenging project for me. I learnt different tools during the project phase. These include designing a communication protocol for a wireless system, programming of an arm processor, \ac{PCB} schematic design and especially their etching in the laboratory. Beside these technical tools, I also leant documentation of a technical project which will be very fruitful for me in future projects. I learn about the different parts of aircraft/spacecraft theoretically but \ac{U-SPACE} provided me the platform to get practical experience of about every subsystems of a satellite. In short, it is a good course which helps to work independently on in the area of personal interest. 
%
\section{Jan}
%
%
\section{Morten}
In overall, the project course was personally for me a useful experience. As a quality/project manager, I experienced many of the typical challenges in project management such as time delays, rephrasing of project goals and system concepts as required, bureaucracy issues, budget constraints, changes in team structure (people leaving, people joining), challenges getting access to components and equipment/labs etc. However, it is also my personal belief that many of these problems could easily have been avoided by better communication and organization with the LTU administration at the beginning of the project. This would allow more advanced (and complete) technical systems to be developed, focusing more on the real technical challenges leading to greater project successes and providing good PR source for LTU and the students when project results are displayed in media. It is my belief that LTU has some great facilities to support very interesting student projects and they should thrive to exploit and nurture this opportunity.
%
Some personal suggestions or comments for future projects:
\begin{itemize}
\item Establishment of Viking room as permanent project room.
\item Always access to a "professional" solder station, possibly even with ESD-protected table + wrist bands.
\item Throughout the project, we were extremely dependent on Lars to get simple components/tools (resistors, wires etc.). This cost us a lot of time, whenever he was not available. If possible, a box of standard components (resistors, capacitors, simple ICs, wires etc.) should be made available to at least one person (if not all) in the project team. A simple account-sheet could be placed next to the box, where people can note what they take.
\item Quicker release of initial project budget to allow first order of components.
\item Access to workshop, once established, worked very well (except some issues with the electronic lock). This access should be established from the beginning of the project.
\item Generally we received good support from IRF, borrowing tools and suggestions for mechanical design. If possible, more instructions and recommendations from IRF experts would be helpful (soldering course, how to check solderings under microscope).
\item More critical design feedback and suggestions from supervisors, where possible, would be good.
\item More clear initial communication of project course requirement in terms of reports and presentations (how many, which and when). Ideally a document should be generated which states all specifications to the project course (budget, reports, flight-options/rules, expected support from IRF and LTU, course rules for non-EU students, course registration if done in spring semester, possibility to order components from foreign countries, etc.).
\item Project budget was not tightly maintained by students in the beginning. But also, some costs (e.g. styrofoam and possibly more) were not communicated to the group and exact amount of budget per student was very unclear throughout most of the project.
\item Especially the Spacemaster students are quite restricted in their time schedule since many of us only have half a year in Kiruna, leaving around June and the rest leaving around January/February the following year. Hence, deadlines and time restrictions stated by these project groups should be well noted and respected.
\end{itemize}